Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-09-18 scagnostics.Rmd
Added CKM example.

(Motivation - something along the lines of the following paragraph, but more understandable, maybe giving concrete example - e.g. dec vs time from neutron star posterior?)
One motivation to consider projection pursuit indices beyond the ones considered so far is coming from physics applications where a standard method is the determination of physcis parameters by means of global fits to large experimental datasets. Typically models will come with a handful of free parameters, model predictions will be calculated by means of numeric tools and the best fit parameters are evaluated by comparing predictions to a large number of observations. Fit results will encode relations between the model parameters dictaded by the available observations, for example if two parameters control predictions for a well constrained observable, looking at the distribution of parameter combinations which are a good fit will be instructive. A standard example is to study the likelihood or posterior distribution in pair-wise 2-d plots, where the selection of parameters if often guided by knowledge of the underlying physics. A major challenge is the progressing complexity in all three aspects: models with larger parameter spaces are being studied, computation of observable predictions is increasingly complex and the number of experimental observations relevant to a given model is growing. Methods for the detection of "interesting" views that can aid physics intuition are therefore more and more relevant.

>>>>

Here we want to extend the list of projection pursuit indices with the aim of detecting non-trivial dependence between parameter combinations, i.e. we want to find complicated functional dependence as well as association not described by a function (e.g. an ellipse or non-coexistence).
Our main motivation stems from particle physics applications where such type of association is commonly implied by experimental and theoretical constraints. A well-studied example would be the so-called CKM triangle. Here an instructive parametrisation is known, and measurements can pin-point the physical value of the parameters. Fig. \ref{fig:CKM} (left) shows a schematic view of the 2-parameter dependence for various constraints. Fig. \ref{fig:CKM} (right) shows the current state of the art constraints.
We expect this type of relations are common in particle physics, and their detection will aid understanding of the relevant physics, and as a consequence improve modelling and parametrisation. The task of uncovering the relevant features is however becoming more challenging as more complicated models are fit to larger sets of experimental results.

\begin{figure}
\includegraphics[width=0.5\textwidth]{figure/CKM-0104062.pdf}
\includegraphics[width=0.5\textwidth]{figure/rhoeta_large_ckmfitter.png}
\caption{CKM triangle constraints, schematic view shown on the left, taken from \cite{Hocker2001xe}, current picture shown on the right, from \cite{Charles2004jd}.}\label{fig:CKM}
\end{figure}
